---
title: "Lab 00 - Hello IDS!"
author: "Louis Newton"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Louis Newton", "Ethan Wood", "Athos Rocha", 
           "Lucas Smith", "Jake Cullen", "Aniruddh Iyer"),
  github_username = c("LouisWeil", "EJamesW05", "athos-roch", 
                      "Is657", "s2543550", "aniruddhviyer"), 
  colour = c("turquoise", "navyblue", "green", 
             "hotpink", "blue", "navyblue"),
  hobby = c("Triathlon", "Reading Novels", "Karting", 
            "Going Out", "Football", "Hiking"),
  favourite_number = c(7, 10, 5, 3, 8, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This plot shows all our team's usernames, colours and favaourite colours.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github_username", 
          y = "favourite_number",
          title = "Favoruite colours and numbers")
```

labs function adds labels to graphs etc.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

This plot isn't useful for showing the data. Perhaps a pie chart would be better at displaying.
